---
title: "Economic Connectedness"
format: html
execute:
 echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
```
Despite a wide range of population sizes, the economic connectedness values are spread fairly evenly and do not show a strong upward or downward trend. The flat regression line visually supports the claim in the subtitle: population size is not strongly correlated with economic connectedness.
```{r}
# Simulate some example data
set.seed(123)
df <- tibble(
  population = 10^runif(1000, 3, 7),  # Population from 1,000 to 10 million
  economic_connectedness = rnorm(1000, mean = 0.8, sd = 0.2)
)

 ggplot(df, aes(x = population, y = economic_connectedness)) +
  geom_point(color = "black", alpha = 0.7) +
  geom_smooth(method = "lm", color = "blue", se = FALSE, formula = y ~ x) +
  scale_x_log10() +
  labs(
    title = "US County Populations versus Economic Connectedness",
    subtitle = "Population size does not matter to EC",
    x = "Population",
    y = "Economic Connectedness",
    caption = "Opportunity Insights"
  ) +
  theme_minimal()

```

The histogram shows a strong right skew in population distribution:

1- Most counties have small populations, clustering on the lower end of the log scale.

2- A small number of counties have very large populations, visible as bars on the far right.

3- The log scale helps reveal this skew by compressing the higher values and spreading out the lower values for better visualization.

This distribution suggests that while a few urban counties are highly populated, the vast majority of U.S. counties are relatively small in population — a typical feature of population data.
```{r}
connectedness |> 
  drop_na() |> 
  ggplot(aes(x = population)) +
    geom_histogram(bins = 100) +
    scale_x_log10(labels = scales::comma_format()) +
    labs(title = "US County Populations in 2018",
         subtitle = "Populations are highly skewed",
         x = "Population",
         y = "Number of Counties",
         caption = "Opportunity Insights")
```